Robots, Are They Overlords or Serf-Laborers?

### 2015-06-15 draft1.tex
Add Hacking and Human Error to Safety Issues

% Add Hacking Section

% Add human proneness to fail and errors in source code. (skepticism and uncanny)

\subsection{Legal and Ethical Issues}
Furthering concerns about their military applications, robots are envisioned to be controlled by an intelligence which will enable them to perceive their surrounding environments where they can interact with objects by themselves.
Thus, robots can be regarded as independent agents.
This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications for AI.
The first fatal accident resulted killing a laborer by a robot is believed to took place in late 70's, in an industrial complex \cite{lin}.
\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failures?"
Since the contemplation of AI and robots indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of their failures?"
Similar to the questions above, there are many questions that governments need to address by creating regulations and laws under which robots will be positioned. \par
Furthermore, many researchers have been questioning whether or not these super-intelligent agents should have duties to society, such as taxing; if so, to what extent governments should give social rights to robots. \citeA{bob} addresses this issue by underlining basic rights and duties of citizens such as taxing and voting.
In other words, not only does AI's legal ramification matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
To address this issue, \citeA{kerb} analyzes Japanese artworks showing futuristic plots based upon robots cohabitating and interacting with humans.
These artworks depicts the very early speculations of social equality between man and machine regarding civil and political rights among.

\subsection{Psychological Challenges and Socio-economic Issues}
Social interaction is what differentiates humans from machines.
However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive within society.
%For instance, before GPS became publicly available, route planning was based upon map-reading and asking directions of the locals.
%In light of this example, AI has become route planning assistant and has decreased the interrelation among individuals.
%According to \citeA{lan}, reformation of our perception towards AI poses misconceptions regarding personhood and promotes loneliness.
%This issue truly matters due to the fact that alienation from the society relies on that misconception.
In light of definitions given in the first section, robots have to interact with their physical environment.
However, such definitions exclude any means of social interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, appears to be decontextualized with regards to definitions provided in the first section.
This discrepancy brings about a major problem on the individual and societal levels.
One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
Even though this issue seems to have a minor flip-side, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood. \par
Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in workplaces, thereby undermining the true value of failures.
Given that failures are one of most essential component of human learning process, superiority of AI tend to discourage individuals to commit any form of actions due to fear of failures. 
This fear impedes the same body of individuals to learn, hindering them completely to trust human judgment .
Depression and other similar psychological challenges are the most profound indicators of the aftermaths of inaccurate definition of AI. \par

>>>>

% Add human proneness to fail and errors in source code. (skepticism and uncanny)
Coupled with the military concerns, human errors in source code is yet another issue impeding roboticists to develop the software.
As computers scientists, fallible human beings, compile millions of lines of code into one perfect software, the risk of emergence of code that makes a robot to prone to fail in any given task is soaring.
A tiny flaw on software level, \citeA{lin} note, can lead to fatal results.

Moreover, hacking has been the most debated issue since the Internet became publicly available.
Along with many other safety issues, hacking is an associated one regarding how to securely integrate robots in work settings.
In this case, the risk is not identity theft or any other illegal activities since the anticipations for robots to be employed in wide variety of tasks.
If a hacker can grant access in an uncanny way to robots' central processing unit, s/he can make the robot commit any action s/he wants.
So, all the superior abilities \citeA[p.~4]{lin}, namely, "its strength, ability to access and operate in difficult environments, expendability and so on", may be turned against society.
This possibility clearly contradicts the ultimate goal of creation of robots.

 \subsection{Legal and Ethical Issues}
 Furthering concerns about their military applications, robots are envisioned to be controlled by an intelligence which will enable them to perceive their surrounding environments where they can interact with objects by themselves.
Thus, robots can be regarded as independent agents.
This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications for AI.
The first fatal accident resulted killing a laborer by a robot is believed to took place in late 70's, in an industrial complex \cite{lin}.
\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failures?"
Since the contemplation of AI and robots indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of their failures?"
Similar to the questions above, there are many questions that governments need to address by creating regulations and laws with which robots will comply. \par
Furthermore, many researchers have been questioning whether or not these super-intelligent agents should have duties to society, such as taxing; if so, to what extent governments should give social rights to robots. \citeA{bob} addresses this issue by underlining basic rights and duties of citizens such as taxing and voting.
In other words, not only does AI's legal ramification matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
To address this issue, \citeA{kerb} analyzes Japanese artworks showing futuristic plots based upon robots cohabitating and interacting with humans.
These artworks depicts the very early speculations of social equality between man and machine regarding civil and political rights among.

\subsection{Psychological Challenges and Socio-economic Issues}
Social interaction is what differentiates humans from machines.
However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive within society.
%For instance, before GPS became publicly available, route planning was based upon map-reading and asking directions of the locals.
%In light of this example, AI has become route planning assistant and has decreased the interrelation among individuals.
%According to \citeA{lan}, reformation of our perception towards AI poses misconceptions regarding personhood and promotes loneliness.
%This issue truly matters due to the fact that alienation from the society relies on that misconception.
In light of definitions given in the first section, robots have to interact with their physical environment.
However, such definitions exclude any means of human interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, appears to be decontextualized with regards to definitions provided in the first section.
This discrepancy brings about a major problem on the individual and societal levels.
One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
Even though this issue seems to have a minor flip-side, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood. \par
Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in workplaces, thereby undermining the true value of failures.
Given that failures are one of most essential component of human learning process, superiority of AI tend to discourage individuals to commit any form of actions due to fear of failures. 
This fear impedes the same body of individuals to learn, hindering them completely to trust human judgment .
Depression and other similar psychological challenges are the most profound indicators of the aftermaths of inaccurate definition of AI. \par
